Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-13 paper.qmd
Fix the issue and mnist digit1 best model added

@@

<!-- Fit the model and compute error-->
```{r}
## Compute hexbin parameters
num_bins_x_mnist <- 20
lim1 <- mnist_scaled_obj$lim1
lim2 <- mnist_scaled_obj$lim2
r2_mnist <- diff(lim1)/diff(lim2) # Need to correct r2_mnist <- diff(lim2)/diff(lim1)

@@

## To join embedding
error_df <- error_df |>
  bind_cols(pacmap_minst |> 
              select(-ID))

@@

```{r}
#| echo: false
#| fig-cap: "(a) Model generated in the 2D space overlaid on PaCMAP data, and (b) high-D model error in model space."
#| label: fig-model-mnist
#| fig-pos: H

@@

imge_error_sample <- pixels_gathered |> 
  ggplot(aes(x, y, fill = value)) +  
  geom_tile() +  
  facet_wrap(~ instance, ncol = 5) +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank())
```

>>>>

<!-- UMAP layout with author's suggested parameter choice-->
```{r}
## Import data
training_data_pbmc <- read_rds("data/pbmc3k/pbmc_pca_50.rds")
training_data_pbmc <- training_data_pbmc[, 1:9] |>
  mutate(ID = 1:NROW(training_data_pbmc))

umap_pbmc <- read_rds("data/pbmc3k/pbmc_umap_30_min_dist_0.3.rds")
pbmc_scaled_obj <- gen_scaled_data(
  data = umap_pbmc)
umap_pbmc_scaled <- pbmc_scaled_obj$scaled_nldr

umap_pbmc <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.5) 
```

<!-- UMAP parameters suggested by the author(n_neighbors = 30, min_dist = 0.3)-->
```{r}
#| fig-cap: "2D layout from UMAP applied for the PBMC3k dataset. Is this a best representation of the original data?"
#| label: fig-umapauthor
#| fig-width: 3
#| fig-height: 3
#| fig-pos: H

umap_pbmc 
```

@@

<!-- Fit the model and compute error-->
```{r}
## Compute hexbin parameters
num_bins_x_mnist <- 37
lim1 <- mnist_scaled_obj$lim1
lim2 <- mnist_scaled_obj$lim2
r2_mnist <- diff(lim2)/diff(lim1)

@@

## To join embedding
error_df <- error_df |>
  bind_cols(pacmap_minst_scaled |> 
              select(-ID))

@@

<!--bin1 = 37, bin2 = 26, b = 962, non_empty = 398-->
```{r}
#| echo: false
#| fig-cap: "(a) Model generated in the 2D space overlaid on PaCMAP data, and (b) high-D model error in model space."
#| label: fig-model-mnist
#| fig-pos: H

@@

imge_error_sample <- pixels_gathered |> 
  ggplot(aes(x, y, fill = value)) +  
  geom_tile() +  
  facet_wrap(~ instance, ncol = 2) +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank())
```
